%\subsection{Motivation}

% Motivação: contextualização do problema ou da necessidade que motivou o trabalho. Essa seção deve preparar o leitor para a <Pergunta da Pesquisa>

According to the World Health Organisation (WHO) on the , there are at least 2.2 billion people with some visual impairment degree (\cite{world2019world}. Among them, 43,3 million are classified as blind and 295 million have moderate or severe vision impairment. In order to be fully integrated into our society, they rely on assistive devices, such as canes, braille speakers, among others \cite{bourne2021trends}. 

Although a range of products has already been proposed, incorporating different features, they do not entirely fulfill their aim. Among the problems, of the solutions available in the market, are the lack of practicality and portability, invasive and requiring too much effort to learn \cite{lozano2009electrotactile}.

The difficulty of using or learn how to use a device could be avoided if concepts from Human Factors, or Ergonomics, were analysed during the product’s development, using appropriate methods. The early application of these methods and tests could be a gamechanger for the success of the product's user experience \cite{wolf2019towards}.

Motivated by the dissatisfaction of blind people with the currently available products, this paper starts from the hypothesis that a human-factors-centred design of assistive devices for blind and visually impaired people (BVIs) requires the involvement of BVIs in the design process in order to evaluate the product under design. The user has to test the product under development to provide feedback for the design team to improve the product.

In order to approach this problem, this work proposes using virtual reality (VR) as a tool for creating virtual environments, where proof of concepts or prototypes of assistive devices could be tested by BVIs. VR can be used to create specific, immersive and interactive situations that could help the user to learn and train \cite{farrell2018learning}, and the the developers to create more user-friendly products.

In a virtual environment, as long as the BVI is wearing a locating system, s/he can navigate the environment. Any information about the scenario, such as the position of objects and their distances to the user, is known and could be extracted from the virtual platform. As a consequence the designer can test different ways of translating this information into inputs before actually implementing a prototype of the assistive device, providing a flexible, safe and easy way to have it evaluated by different users.

%\section{Virtual reality in the design process}
\label{sec:vr_cabin}
\input{1 - Introducao/vr_cabin}

%\section{Virtual reality for BVI users}
\label{sec:vr_without_vision}
\input{1 - Introducao/vr_without_vision__siu_et_al}

%\section{Augmented reality for BVI users}
\label{sec:ar_without_vision}
\input{1 - Introducao/ar__kirner}

%\section{Information for BVI navigation}
\label{sec:bradley_dunlop}
\input{1 - Introducao/bradley_dunlop}

%\subsection{Mental Workload (MWL)}
\label{sec:mental_workload}
\input{1 - Introducao/mental_workload}

%\subsection{Situation Awareness (SA)}
\label{sec:situation_awareness}
\input{1 - Introducao/situation_awareness}

%\section{Co-Design}
\label{sec:co_design}
\input{1 - Introducao/co_design}

This paper's main goal is the use of virtual reality as a tool for evaluating proofs of concept of assistive devices for blind and visually impaired people from a human-factors perspective. The purpose is to provide a flexible and easily configured way of testing different concepts of assistive devices in order to support an agile and user-centered development.

This goal is related to the following research questions, which are investigated in this work:

\begin{itemize}
   \item Is it possible to evaluate and compare concepts of assistive devices from a human factors perspective in a virtual environment? What are the main limitations of the use of a virtual reality environment? \label{itm:obj_first}
   \item Do non-BVI users, when deprived of their vision, similarly evaluate assistive devices as BVI users? \label{itm:obj_second}
\end{itemize}

% Delimitação da pesquisa: é o recorte do seu trabalho

The concepts of assistive devices presented as part of this work are used only as examples for investigating the research questions presented. The challenges related to their full development up to high Technology Readiness Levels (TRLs), as well as their feasibility as commercial products, are out of the scope of this work.

% Estrutura do texto

\subsection*{Structure of the text}

The next Section of this paper are organized as follows.

Section \ref{ch:metodologia} details the proposal of this paper describing how virtual reality could be used to integrate BVI users into the design process of assistive design. It illustrates the proposed method by applying it to evaluate three different assistive devices (audio guide, virtual cane and haptic belt), as well as their mixed-use, in the environment of a hospital reception. 

Section \ref{ch:resultados} describes the experiment designed to evaluate the paper's proposal and analyses the results in order to investigate the research questions of Section \ref{sec:objetivos}

Finally, section \ref{ch:conclusao} summarizes the main conclusions of this work and discusses future work.
